\todo{Something} presents OpenAdcess

### 2017-02-13 digital-library.tex
added impact factor-ometer

>>>>

\subsection{Impact Factor-ometer}

Researchers want their projects to have meaning and impact. Administrators like to market their department's product as meaningful and impactful. But how can researchers tell their work is saving the world?

Simple. Once a quarter, the Ricketts family convokes Gary Cohn, Dennis Rodman, and the rest of the Economic Advisory Council at Chicago's historic Wrigley Field to make use of the stadium's native Noise-ometer. As Pat Hughes reads the papers over the PA in a Charlie Brotman accent, the council---taking especial care to note the presence of key phrases like ``cross-promotional deal mechanics revenue streams jargon synergy" and ``a strategic planning initiative\ldots with a focus on strategic dynamism"---emits cheers in proportion to its perception of the paper's impact, and these cheers are registered on the Noise-ometer, which assigns metrics of impact to each paper, as shown in Figure \todo{fig:noiseometer}

\begin{figure}
  \centering
  %https://archive.org/details/414803main_0203243
  \includegraphics[width=0.45\textwidth]{figures/noiseometer.jpg}
  \caption{A model-year 1985 Noise-ometer, prized by collectors for its muted design that limns adumbrations of sound. The paper in which these meetings were proposed was met at the first such convening of the Council with a cheer so loud it registered a ``Fuck Yeah!" (not shown) on this scale.}
  \label{fig:vr-mill}
\end{figure}

These metrics empower our research partners to be certain their research is having a real-world impact.  It is important for researchers to know that they don't risk deactivation or exile if they remain on track.
